A Large-scale Study of Polymorphism in R

### 2019-03-18 paper/main.tex
intro

@@

	\item \AT{maybe} a tool to analyze the polymorphicity of R code;

	\item a study of polymorphism in the R language \AT{using said tool};

	\item a number of proposed static type systems for R which cover most of the 
	type usage patterns which arise in R code.

>>>>

This papers is a data-driven study of what a type system for the R language
could look like. Longer term, our intention is to propose changes to
language, but for any changes to be accepted by the user community, they
must clearly benefit the language without endangering backwards
compatibility. Our goal is thus to find a compromise between simplicity and
usefulness; the proposed type system should cover most common programming
idioms while remaining easy to use. In order to do this, we need to
understand the degree of polymorphism present in R code, that is to say, how
programmers leverage the dynamic nature of R to write code that can accept
arguments of different types.  This understanding will drive our design.

@@

\begin{itemize}
\item \AT{maybe} a tool to analyze the polymorphicity of R code;
\item a study of polymorphism in the R language \AT{using said tool};
\item a number of proposed static type systems for R which cover most of the
  type usage patterns which arise in R code.
\end{itemize}
